Parties, Models, Mobsters\newline {\fontsize{11}{15}\selectfont A New Implementation of Model-Based Recursive Partitioning in R}

### 2014-03-13 pkg/partykit/inst/NUS-2014/modelparty.Rnw
Formula refs
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@480 255f4249-2263-4417-b1ea-8498779e27a7
draft of class description
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@486 255f4249-2263-4417-b1ea-8498779e27a7

\begin{frame}[fragile]
\frametitle{Implementation: Class}

\textbf{Class:} `\code{modelparty}'.

FIXME

@@

\footnotesize

@@

Zeileis A, Hothorn T (2014).
 \textit{Parties, Models, Mobsters: A New Implementation of Model-Based Recursive Partitioning in R.}
 \texttt{vignette("mob",~package~=~"partykit")}.

@@

%% \medskip
%% 
%% Rusch T, Lee I, Hornik K, Jank W, Zeileis A (2013).
%%   \dquote{Influencing Elections with Statistics: Targeting Voters with Logistic Regression Trees.}
%%   \textit{The Annals of Applied Statistics}, \textbf{7}(3), 1612--1639.
%%   \doi{10.1214/13-AOAS648}

>>>>

\begin{frame}[fragile]
\frametitle{Implementation: Parties}

\textbf{Class:} `\code{modelparty}' inheriting from `\code{party}'.

\textbf{Main addition:} Data handling for regressor and partitioning variables.
\begin{itemize}
  \item The \emph{Formula} package is used for Two-part formulas, e.g.,\\
    \code{y ~ x1 + x2 | z1 + z2 + z3}.
  \item The corresponding terms are stored for the combined
    model and only for the partitioning variables.
\end{itemize}

\textbf{Reusability:} Could in principle be used for other model trees as well (inferred
by other algorithms than MOB).

\textbf{Additional information:} In \code{info} slots of `\code{party}' and `\code{partynode}'.
\begin{itemize}
  \item \code{call}, \code{formula}, \code{Formula}, \code{terms} (partitioning variables only),
    \code{fit}, \code{control}, \code{dots}, \code{nreg}.
  \item \code{coefficients}, \code{objfun}, \code{object}, \code{nobs}, \code{p.value}, \code{test}.
\end{itemize}

@@

\scriptsize

@@

Zeileis A, Hothorn T (2014).
 \textit{Parties, Models, Mobsters: A New Implementation of Model-Based Recursive Partitioning in R.}
 \texttt{vignette("mob",~package~=~"partykit")}

Zeileis A, Croissant Y (2010).
  \dquote{Extended Model Formulas in R: Multiple Parts and Multiple Responses.}
  \textit{Journal of Statistical Software}, \textbf{34}(1), 1--13. 
  URL~\url{http://www.jstatsoft.org/v34/i01/}

@@

Rusch T, Lee I, Hornik K, Jank W, Zeileis A (2013).
  \dquote{Influencing Elections with Statistics: Targeting Voters with Logistic Regression Trees.}
  \textit{The Annals of Applied Statistics}, \textbf{7}(3), 1612--1639.
  \doi{10.1214/13-AOAS648}
